Can Symmetric Cryptography Be Liberated from the Von Neumann Style?

### 2024-12-12 paper.tex
suboptimal
before hand -> beforehand

Storing only 16 bits in a 32 bits word (on \textsc{Arm} Cortex M)
remains sub-optimal. We can further increase register usage and
instantly double throughput by processing two blocks at the same
time. To this end, we introduce a new Naperian functor,
\coqe!Double.T!, indexed by the two elements set \coqe!Fst!  and
\coqe!Snd!. Since \coqe!Double.T bool! is a Boolean algebra, we immediately get that \coqe!subcells_! and \coqe!add_shift_rows_! can process two blocks at the same time. This leads to
%
\coqfrom{Skinny/Bitslice}{state}
%
which denote our intent to manipulate objects of type \coqe!reg32! as
if they were stored in a single machine word.  In the present work,
this observation will remain at the state of wishful thinking. One can
think of the code in this section (as well as the fixsliced code, in
the next section) as playing, themselves, the role of specifications
to lower-level refinements. Our previous work on Usuba~\citep{mercadier:PhD} suggests that
we will be able to deliver on this promise in the future. Further,
remark that the \coqe!state! now corresponds to two intermingled
blocks but as we shall process them in lock-step throughout the
cipher, this does not make much difference.

@@

Note that we have to transform the input key before hand, so as to
keep both blocks aligned. In particular, this means that we do not
have to correct the first round subkey, we will have to apply
\coqe!inv_phi! to the second round subkey, \coqe!iter 2 inv_phi! to
the third round subkey and, finally, \coqe!iter 3 inv_phi! to the
fourth round subkey. The fifth round subkey starts back in sync,
\etc{}

>>>>

Storing only 16 bits in a 32 bits word (on \textsc{Arm} Cortex M)
remains suboptimal. We can further increase register usage and
instantly double throughput by processing two blocks at the same
time. To this end, we introduce a new Naperian functor,
\coqe!Double.T!, indexed by the two elements set \coqe!Fst!  and
\coqe!Snd!. Since \coqe!Double.T bool! is a Boolean algebra, we immediately get that \coqe!subcells_! and \coqe!add_shift_rows_! can process two blocks at the same time. This leads to
%
\coqfrom{Skinny/Bitslice}{state}
%
which denote our intent to manipulate objects of type \coqe!reg32! as
if they were stored in a single machine word.  In the present work,
this observation will remain at the state of wishful thinking. One can
think of the code in this section (as well as the fixsliced code, in
the next section) as playing, themselves, the role of specifications
to lower-level refinements. Our previous work on Usuba~\citep{mercadier:PhD} suggests that
we will be able to deliver on this promise in the future. Further,
remark that the \coqe!state! now corresponds to two intermingled
blocks but as we shall process them in lock-step throughout the
cipher, this does not make much difference.

@@

Note that we have to transform the input key beforehand, so as to
keep both blocks aligned. In particular, this means that we do not
have to correct the first round subkey, we will have to apply
\coqe!inv_phi! to the second round subkey, \coqe!iter 2 inv_phi! to
the third round subkey and, finally, \coqe!iter 3 inv_phi! to the
fourth round subkey. The fifth round subkey starts back in sync,
\etc{}
